The Eternal Adversary between Censor and Circumvention

### 2024-12-02 paper/paper.tex
fix citation
Do chores and clean some spell issues

% \usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
% Graphic path
% \graphicspath{{./pics/}}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{orcidlink}
\usepackage{hyperref}
\usepackage{multirow}
\usepackage{float}
\usepackage{tikz}
\usetikzlibrary{positioning}
\usepackage{textcomp}
\usepackage{listings}
\usepackage{subcaption}

@@

% \usepackage[
% backend=biber,
% style=IEEEtran,
% sorting=ynt
% ]{biblatex}
% \addbibresource{ref.bib}
\begin{document}

@@

\begin{figure}[!h]
\centering
\input{include/mitm}
\caption{MITM attack: Attacker (M) intercepts messages between client (C) and server (S).}
\label{fig:mitm}
% \vspace{-0.2cm}
\end{figure}

@@

\begin{figure}[!h]
    \centering
    \input{include/fallback}
    \caption{Fallback: Proxy servers filter (P) unauthentic incoming traffic (P) (Probes) and forward it to a real HTTP Server (F) and forward authentic traffic (C) to destination (D)}
    \label{fig:fallback}
\end{figure}

>>>>

% \usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{orcidlink}
\usepackage{hyperref}
\usepackage{multirow}
\usepackage{float}
\usepackage{tikz}
\usetikzlibrary{positioning}
\usepackage{textcomp}
\usepackage{listings}
\usepackage{subcaption}

@@

\begin{document}

@@

\begin{figure}[!h]
\centering
\input{include/mitm}
\caption{MITM attack: attacker (M) intercepts messages between client (C) and server (S).}
\label{fig:mitm}
% \vspace{-0.2cm}
\end{figure}

@@

\begin{figure}[!h]
    \centering
    \input{include/fallback}
    \caption{Fallback: proxy servers filter (P) unauthentic incoming traffic (P) (Probes) and forward it to a real HTTP server (F) and forward authentic traffic (C) to destination (D)}
    \label{fig:fallback}
\end{figure}
